---
title: "Censorship"
author: "Wai Tak Tung, Karolin Schulze"
date: "1/20/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
p_needed <-
  c("knitr",
    "MASS",
    "separationplot",
    "foreign"
  )
packages <- rownames(installed.packages())
p_to_install <- p_needed[!(p_needed %in% packages)]
if (length(p_to_install) > 0) {
  install.packages(p_to_install)
}
sapply(p_needed, require, character.only = TRUE)
library(stargazer)
install.packages(c('tibble', 'dplyr', 'readr'))
library("readxl")
library("dplyr")

```

```{r, warning=FALSE, echo=FALSE}

rm(list = ls())

controls <- read.csv("Control_var.csv")
controls <- controls[,-1]
Approval <- read.csv("Approval.csv")
Approval <- Approval[,-1]
Media <- read.csv("Media Freedom.csv")
Media <- Media[,-1]

```

## Merging Data

```{r, echo=FALSE, warning= FALSE}

dta1 <- left_join(Media, Approval, by=c("Year","Country"))

dta1 <- dta1[dta1$Year>=2008 & dta1$Year <=2018,]

dta2 <- left_join(dta1, controls,by=c("Year","Country"))

dta3<- dta2 %>% distinct(Year,Country, .keep_all = TRUE)
dta3 <-na.omit(dta2)

write.csv(dta3, "Final_dta.csv")
dta <- read.csv("Final_dta.csv")
dta <- dta[,-1]

#exclude bolivia to get a better dataset with polity2 8:10 and better pres:pm
dta[dta$Country=="Bolivia",]
dta <- dta3[-c(34:44),]

write.csv(dta, "Final.csv")
dta <- read.csv("Final.csv")
dta <- dta[,-1]

```


```{r Results}

colnames(dta)

boxplot(dta$internet_censorship)
hist(dta$internet_censorship)
boxplot(dta$media_censorship)
hist(dta$media_censorship)
boxplot(dta$Approval_Rate)
hist(dta$Approval_Rate)
boxplot(dta$Internet)
boxplot(dta$GDP_per_capita)
hist(dta$media_corrupt)

barplot(dta$Approval_Rate)

plot(dta$int_filt_cap,
     dta$int_shut_cap)
abline(lm(dta$int_shut_cap~dta$int_filt_cap))

par(mfrow=c(2,2))
plot(dta$int_filt_cap,
     dta$internet_censorship)
abline(lm(dta$internet_censorship~dta$int_filt_cap))
plot(dta$int_shut_cap,
     dta$internet_censorship)
abline(lm(dta$internet_censorship~dta$int_shut_cap))

#int_filt_cap and int_shut_cap are vitually the same, so drop at least one

#Distribution main variables

pdf("Boxplots.pdf")
par(mfrow = c(2,2))
boxplot((dta$Approval_Rate),
        main = "Public Opinion, 2008-2018",
        xlab = "Government Approval in %")
boxplot(dta$media_censorship,
        main = "Government Censorship, 2008-2018",
        xlab = "Broadcast & Print Media Censorship Effort")
boxplot(dta$internet_censorship,
        main = "Government Censorship, 2008-2018",
        xlab = "Internet Censorship Effort")
boxplot(dta$Internet,
        main = "Internet Users 2008-2018",
        xlab = "% of Internet Users in Population")
dev.off()

pdf("controls_int.pdf")
par(mfrow = c(2,2), pty = "s")
plot(dta$media_bias,
     dta$Approval_Rate)
abline(lm(dta$Approval_Rate~dta$media_bias))
plot(dta$media_corrupt,
     dta$Approval_Rate)
abline(lm(dta$Approval_Rate~dta$media_corrupt))
plot(dta$int_filt_cap,
    dta$internet_censorship)
abline(lm(dta$internet_censorship~dta$int_filt_cap))
plot(dta$int_shut_cap,
     dta$internet_censorship)
abline(lm(dta$internet_censorship~dta$int_shut_cap))
dev.off()

```

```{r}

head(dta)
names(dta)

m1 <- lm(Approval_Rate ~ internet_censorship * Internet + media_censorship, data= dta)

m2 <- lm(Approval_Rate ~ internet_censorship * Internet + media_censorship + media_corrupt, data= dta)

m3 <- lm(Approval_Rate ~ internet_censorship * Internet + media_censorship * media_corrupt + GDP_growth + Resource, data= dta)

summary(m1)
summary(m2)
summary(m3)

head(dta)

stargazer(m1, m2, m3)

#summary statistics

stargazer(dta)

```

```{r}

#marginal effect

pdf("margins.pdf")
pred_lm <- function (b, x, z) {
  preds <- matrix(NA, length(x), length(z))
  for (i in 1:length(z)) {
    preds[, i] <- b[1] + b[2] * x + b[3] * z[i] + b[4] * x * z[i]
  }
  return(preds)
}

b_con <- coef(m3)
x_vals <- seq(min(dta$internet_censorship), max(dta$internet_censorship), length.out = 101)
z_vals_con <- quantile(dta$Internet, 
                       c(0, .01, .1, .25, .5, .75, .9, .99, 1))
preds_con <- pred_lm(b_con, x_vals, z_vals_con)

## Function for marginal effect 

mfx_lm <- function (b, z) {
  b[2] + b[8] * z
}

mfx_con <- mfx_lm(b_con, z_vals_con)

se_mfx <- function (vcov, z) {
  sqrt(vcov[2, 2] + z ^ 2 * vcov[8, 8] + 2 * z * vcov[8, 2])
}

vcov_con <- vcov(m3)
se_mfx_con <- se_mfx(vcov_con, z_vals_con)

plot (
  x = z_vals_con,
  y = mfx_con,
  pch = 16,
  xlab = "Internet Users",
  ylab = bquote(frac(partialdiff ~ y, partialdiff ~ x)),
  type = "n",
  bty = "n",
  las = 1,
  main = "Marginal Effect of Internet Censorship on Approval",
  xlim = c(0, 100),
  ylim = c(-20,30),
  bty = "n"
)
abline(h = 0, col = 'gray60', lwd = .5)


for (i in 1:length(se_mfx_con)) {
  points(x = z_vals_con[i],
         y = mfx_con[i],
         pch = 19)
}
for (i in 1:length(se_mfx_con)) {
  segments(
    z_vals_con[i],
    mfx_con[i] + qnorm(.025) * se_mfx_con[i],
    z_vals_con[i],
    mfx_con[i] + qnorm(.975) * se_mfx_con[i],
    lty = i
  )
}

## Add contiguous lines for mfx and se's to the last plot
## Compute first...
z_vals_fine <-
  seq(min(dta$Internet), max(dta$Internet), length.out = 101)
mfx_fine <- mfx_lm(b_con, z_vals_fine)
se_mfx_fine <- se_mfx(vcov_con, z_vals_fine)

## ... then plot
lines(z_vals_fine, mfx_fine)
lines(z_vals_fine, mfx_fine + qnorm(.025) * se_mfx_fine, lty = 2)
lines(z_vals_fine, mfx_fine + qnorm(.975) * se_mfx_fine, lty = 2)
dev.off()

```

```{r}

#Why censorship of traditional media does not work in democracies?


pdf("media bias & corruption.pdf")
par(mfrow = c(2, 2), # 2 x 2 pictures on one plot
          pty = "s") 
plot(dta$internet_censorship,
     dta$Approval_Rate,
     xlab = "Internet Censorship Effort",
     ylab = "Government Approval")
abline(lm(dta$Approval_Rate~dta$internet_censorship))

plot(dta$government_censorship,
     dta$Approval_Rate,
     xlab = "Broadcast & Print Media Censorship Effort",
     ylab = "Government Approval")
abline(lm(dta$Approval_Rate~dta$government_censorship))

plot(dta$Internet, 
     dta$internet_censorship,
     xlab = "% of Internet Users",
     ylab = "Internet Censorship Effort")
abline(lm(dta$internet_censorship~dta$Internet))

plot(dta$media_corrupt, 
     dta$government_censorship,
     xlab = "Media corruption",
     ylab = "Broadcast & Print Media Censorship Effort")
abline(lm(dta$government_censorship~dta$media_corrupt))
dev.off()

plot(dta$media_bias,
     dta$media_corrupt)
abline(lm(dta$media_corrupt~dta$media_bias))

mm <- lm(dta$government_censorship~dta$media_bias)
summary(mm)

summary(dta$government_censorship)
```


```{r}

#Plot Government Censorshpip

freesk <- dta$government_censorship[dta$Country =="South Korea"]
freejp <- dta$government_censorship[dta$Country =="Japan"]
freeaus <- dta$government_censorship[dta$Country == "Australia"]
freeph <- dta$government_censorship[dta$Country == "Philippines"]
freearg <- dta$government_censorship[dta$Country == "Argentina"]
freebol <- dta$government_censorship[dta$Country == "Bolivia"]
freebr <- dta$government_censorship[dta$Country == "Brazil"]
freeus <- dta$government_censorship[dta$Country == "United States"]
freebul <- dta$government_censorship[dta$Country == "Bulgaria"]
freehu <- dta$government_censorship[dta$Country == "Hungary"]
freefr <- dta$government_censorship[dta$Country == "France"]

summary(dta$government_censorship)

pdf("Government Censorship_plot.pdf")
plot(x = yearsk, 
     y = freesk,
     xlab = "Year", 
     ylab = "Government Censorship",
     xlim = c(2008, 2018), 
     ylim = c(0,3.5),
     pch = 16,
     main = "Freedom of Print and Broadcast Media",
     type = "n")
points(yearsk, freesk, col = 1)
points(yearsk, freejp, col = 2)
points(yearsk, freeaus, col = 3)
legend("bottomright",
       legend = c("South Korea", "Japan", "Australia"),
       col = c(1,2,3), 
       pch = c(16, 16, 16))
dev.off()

#Plot Approval Rate

govsk <- dta$Approval_Rate[dta$Country =="South Korea"]/100
govjp <- dta$Approval_Rate[dta$Country =="Japan"]/100
govaus <- dta$Approval_Rate[dta$Country == "Australia"]/100
govph <- dta$Approval_Rate[dta$Country == "Philippines"]/100
govarg <- dta$Approval_Rate[dta$Country == "Argentina"]/100
govbol <- dta$Approval_Rate[dta$Country == "Bolivia"]/100
govbr <- dta$Approval_Rate[dta$Country == "Brazil"]/100
govus <- dta$Approval_Rate[dta$Country == "United States"]/100
govbul <- dta$Approval_Rate[dta$Country == "Bulgaria"]/100
govhu <- dta$Approval_Rate[dta$Country == "Hungary"]/100
govfr <- dta$Approval_Rate[dta$Country == "France"]/100

summary(dta$Approval_Rate)

pdf("Gov Approval.pdf")
plot(x = govsk, 
     y = yearsk,
     xlab = "Year", 
     ylab = "Approval Rate",
     xlim = c(2008, 2018), 
     ylim = c(0,0.9),
     pch = 16,
     main = "Government Approval")
points(yearsk, govsk, col = 1)
points(yearsk, govjp, col = 2)
points(yearsk, govaus, col = 3)
legend("bottomright",
       legend = c("South Korea", "Japan", "Australia"),
       col = c(1,2,3),
       pch = c(16, 16, 16))
dev.off()

#Internet Censorship

intsk <- dta$internet_censorship[dta$Country=="South Korea"]
intjp <- dta$internet_censorship[dta$Country=="Japan"]
intaus <- dta$internet_censorship[dta$Country == "Australia"]
intph <- dta$internet_censorship[dta$Country == "Philippines"]
intarg <- dta$internet_censorship[dta$Country == "Argentina"]
intbol <- dta$internet_censorship[dta$Country == "Bolivia"]
intbr <- dta$internet_censorship[dta$Country == "Brazil"]
intus <- dta$internet_censorship[dta$Country == "United States"]
intbul <- dta$internet_censorship[dta$Country == "Bulgaria"]
inthu <- dta$internet_censorship[dta$Country == "Hungary"]
intfr <- dta$internet_censorship[dta$Country == "France"]

summary(dta$internet_censorship)

pdf("Internet Freedom.pdf")
plot(x = govsk, 
     y = yearsk,
     xlab = "Year", 
     ylab = "Internet Censorship",
     xlim = c(2008, 2018), 
     ylim = c(-0.3,1.8),
     main = "Freedom of the Internet",
     type = "n")
points(yearsk, intsk, pch = 16, col = 1)
points(yearsk, intjp, pch = 16, col = 2)
points(yearsk, intaus, pch = 16, col = 3)
legend("bottomright",
       legend = c("South Korea", "Japan", "Australia"),
       col = c(1,2,3), 
       pch = c(16, 16, 16))
dev.off()

#Internet Freedom Ordinal
#V-Dem

ordsk <- dta$v2mecenefi_ord[dta$country_name=="South Korea" & dta$year >= 2008]
ordjp <- dta$v2mecenefi_ord[dta$country_name=="Japan" & dta$year >= 2008]
ordaus <- dta$v2mecenefi_ord[dta$country_name=="South Korea" & dta$year >= 2008]
ordarg <- dta$v2mecenefi_ord[dta$country_name=="Japan" & dta$year >= 2008]
ordbol <- dta$v2mecenefi_ord[dta$country_name=="South Korea" & dta$year >= 2008]
ordbul <- dta$v2mecenefi_ord[dta$country_name=="Japan" & dta$year >= 2008]
ordus <- dta$v2mecenefi_ord[dta$country_name=="South Korea" & dta$year >= 2008]
ordbr <- dta$v2mecenefi_ord[dta$country_name=="Japan" & dta$year >= 2008]
ordph <- dta$v2mecenefi_ord[dta$country_name=="South Korea" & dta$year >= 2008]
ordfr <- dta$v2mecenefi_ord[dta$country_name=="Japan" & dta$year >= 2008]
ordhu <- dta$v2mecenefi_ord[dta$country_name=="South Korea" & dta$year >= 2008]

summary(dta$v2mecenefi_ord)

pdf("Internet Freedom East Asia ordinal.pdf")
plot(x = govhk, 
     y = yearhk,
     xlab = "Year", 
     ylab = "Internet Censorship",
     xlim = c(2009, 2020), 
     ylim = c(0,3),
     main = "Freedom of the Internet",
     type = "n")
points(yearsk, freeordsk, pch = 16, col = "blue")
points(yearhk, freeordhk, pch = 16)
points(yearjp, freeordjp, pch = 18, col = "red")
legend("bottomright",
       legend = c("South Korea", "Hong Kong", "Japan"),
       col = c("blue", "black", "red"), 
       pch = c(16, 16, 18))
dev.off()

colnames(dta)

usesk <- dta$Internet[dta$Country=="South Korea"]
usejp <- dta$Internet[dta$Country=="Japan"]
useaus <-dta$Internet[dta$Country == "Australia"]
useph <- dta$Internet[dta$Country == "Philippines"]
usearg <-dta$Internet[dta$Country == "Argentina"]
usebr <- dta$Internet[dta$Country == "Brazil"]
useus <- dta$Internet[dta$Country == "United States"]
usebul<- dta$Internet[dta$Country == "Bulgaria"]
usehu <- dta$Internet[dta$Country == "Hungary"]
usefr <- dta$Internet[dta$Country == "France"]

pdf("Internet users.pdf")
plot(yearsk,
     usesk,
     xlab = "Year",
     ylab = "Internet Users in % of Population",
     main = "Percentage of Internet Users among Population, 2008-2018",
     ylim = c(0,100),
     type = "n")
points(yearsk, usesk, pch = 20, col = 1)
points(yearsk, usejp, pch = 20, col = 2)
points(yearsk, useaus, pch = 20, col = 3)
points(yearsk, useph, pch = 20, col = 4)
points(yearsk, usearg, pch = 20, col = 5)
points(yearsk, usebr, pch = 20, col = 6)
points(yearsk, useus, pch = 20, col = 7)
points(yearsk, usebul, pch = 20, col = 8)
points(yearsk, usehu, pch = 20, col = 9)
points(yearsk, usefr, pch = 20, col = 10)
legend ("bottomright",
        legend = c("KOR", "JPN", "AUS", "PHL", "ARG", "BRA", "USA", "BG", "HU", "FRA"),
       col = c(1, 2, 3, 4, 5, 6, 7, 8, "darkorange", "darkmagenta"), 
       pch = c(20, 20, 20, 20, 20, 20, 20, 20, 20, 20), 
       cex = 0.8)
dev.off()

